%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {IEEE Computer Society} % Job title
    {Events Lead Execom} % Organization
    {NIE IEEE Student Branch} % Location
    {November 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Master Of Ceremony and Convener, All Karnataka Computer Society Congress 2018, NIE Mysuru.}
        \item {Organized Weekly Meetups, where avid programmers are given hands on with technologies: Git, HTML, FOSS, Linux.}
        \item {Project Drive Lead, built a Linux Operating System customized for programmers from scratch based on Arch Linux.}
         \item {Organized Code Golf, a competition where participants had to solve the problem statements and come up with code with shortest number of lines while being time efficient during runtime, the competition was hosted on competitive coding website \href{https://www.hackerrank.com}{www.hackerrank.com}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Onyx, E-Cell} % Job title
    {Campus Venture Pod Head} % Organization
    {National Institute Of Engineering} % Location
    {May 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organized a host of events to spark the spirit of entrepreneurship among fellow members. Events : Rags To Riches, City Ville, Debaited, Crazy Commercials and Jack And Bean Stock.}
        \item {Organized B-Gyaan, National Level Business Plan Competition,NIE Mysuru 2017.}
        \item {Presented a Business Plan before a panel of venture capitalist and entrepreneurs, B-Gyaan. Nourish is an app/platform which aims to provide high quality nutritional food at affordable prices and cater to specific nutritional needs of fitness freaks and strict diet followers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NIE IEEE Student Branch} % Job title
    {IEEE Volunteer} % Organization
    {National Institute of Engineering} % Location
    {Jan. 2013 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organized Competitive Coding competitions like Oculus, Woman In Engineering and IEEE Premier League 8.0 and 9.0 .\href{https://www.hackerrank.com/ieee-premier-league}{www.hackerrank.com/ieee-premier-league}}
        \item { Co developed, IEEE Student Branch Android App.Features include : Events Notification, Blog, Membership details and Event Attendance.
\href{http://github.com/nisbweb/app}{github.com/nisbweb/app}}
        \item {Web Development Team, IEEE Bangalore Section.
\href{www.ieeebangalore.org/}{www.ieeebangalore.org/}}
    \item {Mentored and Organized Basic Programming Session through IEEE Computer Society.First year students were taught C and C++.}
    \item {Played a active role in technical fests like Adroit'16,Exebit'17,Ankura'17,Adroit'17 and Ankuara'18.
Teams Worked : Marketing, On ground Publicity, Tech, Event Management, Master Of Ceremony.}
    \item {Lead the Social Media Team for All Karnataka Computer Society Congress 2018,NIE Mysuru.
\newline{}\href{https://www.instagram.com/akcsc18/}{https://www.instagram.com/akcsc18/} }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NIE IEEE Student Branch} % Job title
    {Android Focus Group Lead} % Organization
    {National Institute of Engineering} % Location
    {Nov. 2017 - Present} % Date(s)
    {}

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
